---
title: "Homework 2"
author: "Varun Saxena"
format:
  pdf:
    output-file: "saxena-v-hwk2-1"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---

Repository: https://github.com/varunsaxena2/saxena-v-hwk2-2/tree/main

\noindent 1. Here is the line graph with the number of hospitals filing multiple reports per year
```{r}
#| echo: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra)

library(knitr)
#library(ggbeeswarm)

load("Hwk2_workspace.Rdata")

ggplot(num_hospitals_multiple_reports, aes(x = year, y = num_hospitals)) +
  geom_line() + 
  labs(x = "Year", y = "Number of Hospitals", title = "Number of Hospitals with Multiple Reports")
```

\newpage
\noindent 2. The number of unique hospitals based on the hospital ID is `r distincthost`.

\newpage
\noindent 3. 

```{r}
#| echo: false
viol1
```

\newpage
\noindent 4. 
``` {r}
#| echo: false

viol2
```

\newpage
\noindent 5.
The average price among penalized hospitals is `r round(penalized[2,2])`. The average price among non-penalized hospitals is `r round(penalized[1,2])`.

\newpage
\noindent 6.

``` {r}
#| echo: false
bedsize
```
\newpage
\noindent 7. 
``` {r} 
#| echo: false
results_table
```

\newpage
\noindent 8. The results are practically identical between the four estimators. This result is quite surprising, as I expected some variance between the estimators.

\newpage
\noindent 9. Not exactly. I think that the differences associated with the penalty may or may not be a direct result on the penalty itself. In other words, the causality of this analysis cannot be determined. However, there is a notable discrepancy between the penalized and non-penalized hospitals, so causality cannot be ruled out.

\newpage
\noindent 10. So far, I have been able to figure out everything fairly well. The violin plots would ideally be formatted better, but I am still figuring out the best way to do that. Also, the tibble for 6 and datafame for 7 would ideally look neater if I knew how to make them more presentable.
